### 2021-05-10 papers/SYRCoSE/overview.tex
expand a bit on relation algebra

In fact, binary relations are omnipresent in our formalization.
In order to further automate the reasoning about them, 
we have chosen to use the \relationalgebra%
\footnote{\url{https://github.com/damien-pous/relation-algebra}}~%
\cite{Pous-ITP2013} package 
which provides a number of tactics to solve goals using
decision procedures for the theory of lattices  
and \emph{Kleene Algebras with Tests}~\cite{Kozen:TOPLAS:1997}.

>>>>

In fact, binary relations are omnipresent in our formalization.
This quickly manifested in a substantial amount of proof overhead and
we seeked for tools to automate our proofs.
Since binary relations form a \emph{Kleene Algebra with Tests}~(KAT)~\cite{Kozen:TOPLAS:1997},
we have chosen to use the \relationalgebra%
\footnote{\url{https://github.com/damien-pous/relation-algebra}}~%
\cite{Pous-ITP2013} package 
which provides a number of tactics to solve goals using
decision procedures for a number of theories, such as
partially ordered monoids, lattices, residuated Kleene allegories and KATs.
